LAGOS lake depth

### 2020-02-28 figures/02_depth_model.Rmd
rounding in metrics table

```{r depth_model_metrics}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds")
jsta::pdf_table(dt_metrics, "../tables/depth_model_metrics-1.pdf")
```

>>>>

```{r depth_model_metrics}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  dplyr::select(slope, dist, everything(), -.estimator)

jsta::pdf_table(dt_metrics, "../tables/depth_model_metrics-1.pdf")
```
